\documentclass{beamer}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{palatino}
\usepackage{ulem}

\title{Jonathan's \emph{Incremental} (Edu)SAT Solver}
\author{Jonathan Reicher}
\institute{Technion}
\date{2025}

\begin{document}

\frame{ \titlepage }

\begin{frame}
    \frametitle{Introduction}
    For this project, I have decided to extend EduSAT to support incremental
    SAT solving. Incremental SAT solving are useful for:
    \begin{itemize}
        \item Evolving problems.
        \item Reachability \& Search (e.g. model checking - very interesting).
        \item Optimization (e.g. Find a solution. Now find a solution that is better).
        \item And more.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Main Challenges}
    \begin{itemize}
        \item Need to support a new interface (adding, removing, disabling clauses).
        \item How to enable/disable clauses.
        \item Testing.
    \end{itemize}
    This are the main challenges I faced in the project so far. I will present
    the current state of handling each challenge.
\end{frame}

\begin{frame}
    \frametitle{The New Interface}
    \begin{itemize}
        \item void read\_cnf(ifstream\& in);
        \item Key addClause(const vector<int>\& clause);
        \item \only<1>{void removeClause(Key key);} \only<2->{\sout{void removeClause(Key key);}}
        \item void enableClause(Key key);
        \item void disableClause(Key key);
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{How to Enable/Disable Clauses}
    \begin{itemize}
        \item<2-> We have seen this!
        \item<3-> Add an \emph{assumption} (selector) variables. These are variables that
            are set to true when to enable a specific clause.
            $$
            (x_1 \lor x_2 \lor \dots \lor x_n)
            \underset{becomes}{\Longrightarrow}
            (\neg t_1 \lor x_1 \lor x_2 \dots \lor x_n)
            $$
            Force $t_1$ to true to enable this clause.
        \item<4-> Need to add special treatment for assumptions in the solver.
            In particular, when adding a clause we add an assumption, and keep
            track of all assumptions, and force some assumptions to be true.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Testing}
    How do I know that my implementation does not have a bug?
    \begin{itemize}
        \item Ipasir - from the famous SAT competition.
        \item Dealt with two kinds of bugs: Performance and correctness.
    \end{itemize}
    Invariant: EduSAT Incremental accepts $\iff$ EduSAT accepts.
\end{frame}

\begin{frame}
    \frametitle{Future Work}
    \begin{itemize}
        \item Run Azure
        \item Run all of Ipasir's tests.
        \item Add more features.
    \end{itemize}
\end{frame}

\end{document}
